### 2015-05-14 evaluation.tex
update in evaluation

\noindent\textbf{Other Tools }
%
We tried to compare \whoop with other similar approaches (see \S\ref{related}). However, we found this hard to achieve, as some tools are not freely available, while others are outdated for several years and are not working on the 4.0 Linux drivers.

>>>>

\noindent\textbf{Other Tools }
%
We tried to compare \whoop with other similar approaches (see \S\ref{related}). However, we found this hard in practice: we downloaded Locksmith~\cite{pratikakis2006locksmith}, but could not get it to work with the 4.0 Linux drivers (the tool was last updated in 2007 and might miss some of the latest features); we also could not find source code or binaries for \cite{kahlon2007fast, kahlon2009semantic, das2015section}.
